GVN-Hoist: Hoisting Computations from Branches

### 2016-08-23 hoist.tex
adding author
fix author alignment
some fixes to introduction

\author{
\alignauthor
Aditya Kumar\\
       \affaddr{Samsung Austin R\&D Center}\\
       \email{aditya.k7@samsung.com}
\alignauthor
Sebastian Pop\\
       \affaddr{Samsung Austin R\&D Center}\\
       \email{s.pop@samsung.com}
}

\maketitle
\begin{abstract}
  Code hoisting identifies identical computations across the program with the
  help of a Global Value Numbering (GVN) analysis, identifies a hoisting
  position that dominates all the identical computations and in which all
  operands are avaialable, duplicates one of the expressions in the hoisting
  position, and removes all the computations now redundant in their original
  position.

  Code hoisting is often confused with CSE (Common Subexpression Elimination)
  although hoisting is not bound to find redundancies within a single basic
  block.  Code hoisting could also be confused with Partial Redundancy
  Elimination (PRE) or with Global Common Subexpression Elimination (GCSE)
  although the main goal of code hoisting is not to remove redundancies: code
  hoisting effectively exposes redundancies and enables other passes like LICM
  to remove more redundancies.  The main goal of code hoisting is to reduce code
  size with the added benefit of exposing more instruction level parallelism and
  reduced register pressure.
\end{abstract}

@@

This paper describes code hoisting, a technique that uses the information
computed for PRE to detect identical computations and has a transformation phase
whose goal differs from PRE: it removes identical computations from different
branches of execution.  These identical computations would not be redundant at
run-time and as the number of run-time computations is not reduced, code
hoisting is not a redundancy elimination pass. This is also different from
global code scheduling \cite{dragonbook} in the sense that code-hoisting will
only hoist computations when there are two or more identical computation sharing
a common dominator. The goals of code hoisting are:

@@

The main contributions of this paper are:
\begin{itemize}
\item a new algorithm to hoist computations from branches,
\item cost model to reduce live-range and reduce spills,
\item performance evaluation of the implementation in LLVM,
\item comparison against other algorithms for code hoisting.
\end{itemize}

>>>>

\author{
\alignauthor
Aditya Kumar\\
       \affaddr{Samsung Austin R\&D Center}\\
       \email{aditya.k7@samsung.com}
\alignauthor
Sebastian Pop\\
       \affaddr{Samsung Austin R\&D Center}\\
       \email{s.pop@samsung.com}
\and
\alignauthor
Daniel Berlin\\
       \affaddr{Google Inc.}\\
       \email{dberlin@dberlin.org}
}

\maketitle
\begin{abstract}
  Code-hoisting identifies identical computations across the program with the
  help of a Global Value Numbering (GVN) analysis, identifies a hoisting
  position that dominates all the identical computations and in which all
  operands are avaialable, duplicates one of the expressions in the hoisting
  position, and removes all the computations now redundant in their original
  position.

  Code-hoisting is often confused with CSE (Common Subexpression Elimination)
  although code-hoisting is not bound to find redundancies within a single basic
  block.  Code-hoisting could also be confused with Partial Redundancy
  Elimination (PRE) or with Global Common Subexpression Elimination (GCSE)
  although the main goal of code-hoisting is not to remove redundancies:
  code-hoisting effectively exposes redundancies and enables other passes like
  LICM to remove more redundancies.  The main goal of code-hoisting is to reduce
  code size with the added benefit of exposing more instruction level
  parallelism and reduced register pressure.
\end{abstract}

@@

This paper describes code-hoisting, a technique that uses the information
computed for PRE to detect identical computations and has a transformation phase
whose goal differs from PRE: it removes identical computations from different
branches of execution.  These identical computations in different branches of
execution are not redundant computations at run-time and the number of run-time
computations is not reduced. Code-hoisting is not a redundancy elimination pass,
and thus it has different cost function and heuristics than PRE or CSE.
Code-hoisting is also different from global code scheduling
\cite{dragonbook,click1995global} in the sense that code-hoisting will only
hoist computations when there are identical computations sharing a common
dominator. The goals of code hoisting are:

@@

The main contributions of this paper are:
\begin{itemize}
\item a new algorithm to hoist computations from branches,
\item cost models to reduce live-range and reduce spills,
\item performance evaluation of the implementation in LLVM,
\item comparison against other algorithms for code hoisting.
\end{itemize}
